---
title: "Chapter 1 Facets"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require("tidyverse")
```

1. What happens when you facet on a continuous variable ?

```{r}
ggplot(data=mpg) +
  geom_point(mapping=aes(x=displ,y=hwy)) +
  facet_wrap(~cty)
```

2. Comparing the two graphs below

```{r}
ggplot(data=mpg)+
  geom_point(mapping=aes(x=displ,y=hwy))+
  facet_grid(drv~cyl)
```

```{r}
ggplot(data=mpg) +
  geom_point(mapping=aes(x=drv,y=cyl))
```

It is clear that no points exist within that subset of data for the combination of drive type and cylinder.

3. By using a . you can suppress either the row dimension or the column dimension.

```{r}
ggplot(data=mpg)+
  geom_point(mapping=aes(x= displ,y=hwy))+
  facet_grid(drv ~ .)
```


```{r}
ggplot(data=mpg)+
  geom_point(mapping=aes(x=displ,y=hwy))+
  facet_grid(.~cyl)
```

4. The advantage is that it is easier to look at trends in the subset of data. 

The disadvantage is that with a color aesthetic since all the point remain on the same graph , it is easier to look at the position of each point with respect to all the other points.

With a larger dataset it would be better to use facetting because with larger datasets the distinction amidst colors become more and more difficult to discern.


```{r}
ggplot(data=mpg)+
  geom_point(mapping=aes(x=displ,y=hwy))+
  facet_wrap(~class,nrow=2)
```