---
title: "Chapter 1 - Aesthetic Mappings"
author: "Aravind A"
date: "20/01/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, error = TRUE)
require("tidyverse")
```

1. 

```{r}
ggplot(data = mpg) +
  geom_point(
    mapping=aes(x=displ,y=hwy,color='blue'))
```

ggplot considers color as a categorical variable with value blue. In order to change the aestheitc of the point to blue color , it is necessary to put in color = blue outside the  mappping construct such as

```{r}
ggplot(data = mpg) +
  geom_point(
    mapping=aes(x=displ,y=hwy),color='blue')

```

2. 

```{r}
mpg
```

Any variable labelled as <chr> is categorical. Other variables labelled as <int> or <dbl> are continuous.

3.

Mapping a continuous variable cty to color

```{r}
ggplot(data = mpg) +
  geom_point(
    mapping=aes(x=displ,y=hwy,color=cty))
```

```{r}
ggplot(data = mpg) +
  geom_point(
    mapping=aes(x=displ,y=hwy,size=cty))
```

```{r}
ggplot(data = mpg) +
  geom_point(
    mapping=aes(x=displ,y=hwy,shape=cty))
```


Mapping a categorical variable

```{r}
ggplot(data = mpg) +
  geom_point(
    mapping=aes(x=displ,y=hwy,color=model))
```

```{r}
ggplot(data = mpg) +
  geom_point(
    mapping=aes(x=displ,y=hwy,shape=model))
```

```{r}
ggplot(data = mpg) +
  geom_point(
    mapping=aes(x=displ,y=hwy,size=model))
```







4. Mapping the same variable to multiple aesthetics. It just ends up creating a lot og clutter in the plaot

```{r}
ggplot(data = mpg) +
  geom_point(
    mapping=aes(x=displ,y=hwy,color=trans,shape=trans,size=trans))
```



5. Stroke changes the border for shapes 21-24 

6.It treats the output of displ  < 5 which is TRUE or FALSE and makes that categorical as well

```{r}
ggplot(data = mpg) +
  geom_point(
    mapping=aes(x=displ,y=hwy,color=displ < 5))
```
